%-------------------------
% Pradnya Patil Resume in Latex
% Based on Tushar Patil's template
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\large#3} & \textit{\large #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\large#1} & \textit{\large #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \large#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-2pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2pt}}

\setlength{\footskip}{4.08003pt}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}


\begin{center}
    \textbf{\Huge \scshape Pradnya Tanaji Patil} \\ \vspace{1pt}
    \large \href{tel:+917517034453}{\underline{+91 7517034453}} $|$ \href{mailto:patilpradnya919@gmail.com}{\underline{patilpradnya919@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/pradnya-patil-643b6427a}{\underline{LinkedIn Profile}}
\end{center}


%-----------Summary-----------
\section{Summary}
    Recent \textbf{B.Tech graduate} in Electronics \& TeleCommunication Engineering with hands-on experience in \textbf{embedded systems}, \textbf{Arduino programming}, and \textbf{Python}. Demonstrated expertise through multiple internships and academic projects focused on safety systems and automation. Passionate about applying technical skills to solve real-world problems and eager to contribute to innovative engineering solutions.


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Shree Siddheshwar Women's College of Engineering}{Solapur, MH}
      {Bachelor of Technology (Electronic \& TeleCommunication)}{August 2022 -- June 2025}
      \resumeItemListStart
        \resumeItem{CGPA: 65.40\% under DBATU}
      \resumeItemListEnd
    \resumeSubheading
      {Shree Siddheshwar Women's Polytechnic}{Solapur, MH}
      {Diploma in Engineering}{July 2019 -- June 2022}
      \resumeItemListStart
        \resumeItem{Percentage: 71.41\% under MSBTE}
      \resumeItemListEnd
    \resumeSubheading
      {Gandhi Natha Rangji Vidyalaya}{Solapur, MH}
      {SSC - Maharashtra State Board}{2018 -- 2019}
      \resumeItemListStart
        \resumeItem{Percentage: 75.60\%}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \large{\item{
     \textbf{Programming Languages}{: Python, C Programming, HTML, CNC Programming} \\
     \textbf{Development Tools}{: Arduino IDE, MS Excel, PLC} \\
     \textbf{Hardware Skills}{: Embedded systems, Arduino} \\
     \textbf{Soft Skills}{: Problem-Solving, Adaptability, Presentation Skills}
    }}
 \end{itemize}
 

%-----------EXPERIENCE-----------
\section{Internships \& Training}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Graduate Trainee Engineer}{Jan 2025 - June 2025}
      {Bajaj Engineering Skill Training CSR Program (BEST)}{Pune, MH}
      \resumeItemListStart
        \resumeItem{Participated in comprehensive engineering skill development program focusing on industry best practices.}
        \resumeItem{Gained exposure to manufacturing processes and quality control systems.}
        \resumeItem{Completed training modules on Total Productive Maintenance (TPM) methodologies.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Trainee Engineer}{July 2024}
      {TechnoHacks EduTech}{Solapur, MH}
      \resumeItemListStart
        \resumeItem{Worked on technical projects involving software development and system design.}
        \resumeItem{Collaborated with team members on educational technology solutions.}
        \resumeItem{Enhanced problem-solving skills through hands-on project experience.}
      \resumeItemListEnd

    \resumeSubheading
      {Trainee Engineer}{2021}
      {Spoken Tutorial, IIT Bombay}{India}
      \resumeItemListStart
        \resumeItem{Completed structured learning modules on various technical topics.}
        \resumeItem{Developed foundational skills in programming and system design.}
        \resumeItem{Participated in online learning initiatives and skill assessments.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Academic Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
            {\textbf{Service Robot Controlled by Google Assistant and Arduino} $|$ \emph{Arduino, C++, Ultrasonic Sensors}}{}
            \resumeItemListStart
              \resumeItem{Built an Arduino-based robot capable of autonomous movement.}
              \resumeItem{Integrated ultrasonic sensor for real-time object detection.}
              \resumeItem{Created a self-navigating robot using Arduino and ultrasonic sensors.}
              \resumeItem{Assembled hardware including motors, wheels, and driver module.}
              \resumeItem{Coded motor control and distance sensing algorithms in C++.}
            \resumeItemListEnd
      \resumeSubHeadingListEnd
      \resumeProjectHeading
          {\textbf{Night Patrolling Device with Arduino} $|$ \emph{Arduino, C Programming, Embedded Systems}}{}
          \resumeItemListStart
            \resumeItem{Designed and developed a comprehensive night patrolling system to enhance safety and security during night-time hours.}
            \resumeItem{Implemented motion detection technology to identify unauthorized movement or intrusions in monitored areas.}
            \resumeItem{Integrated alarm and buzzer systems that activate automatically when motion is detected.}
            \resumeItem{Developed notification system capable of sending alerts and making calls to owners or security personnel.}
            \resumeItem{Utilized Arduino micro-controller for system control and sensor integration.}
            \resumeItem{Tested and validated system performance under various environmental conditions.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Alcohol Detector and Engine Locking System} $|$ \emph{Arduino, MQ-3 Sensor, Embedded Systems}}{}
          \resumeItemListStart
            \resumeItem{Developed an innovative vehicle safety mechanism that prevents engine start if the driver is intoxicated.}
            \resumeItem{Integrated MQ-3 alcohol sensor sensitive to alcohol vapors in breath for accurate detection.}
            \resumeItem{Programmed Arduino to process analog signals from alcohol sensor based on concentration levels.}
            \resumeItem{Implemented relay-based engine locking system that activates when alcohol levels exceed safety threshold.}
            \resumeItem{Designed user-friendly interface with clear indicators for system status and alerts.}
            \resumeItem{Conducted extensive testing to ensure reliable operation and safety compliance.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------Certifications-----------
\section{Certifications}
    \begin{itemize}
        \item \textbf{PCB and Drone Designing} - Aptron Tech
        \item \textbf{Python Fundamentals} - Great Learning
        \item \textbf{Manufacturing System Program on TPM} - Bajaj
        \item \textbf{Workshop on Metaverse} - Technology Workshop
        \item \textbf{Soft Skills Course} - NPTEL
        \item \textbf{Employability Skill Training Program} - Naandi Foundation
    \end{itemize}


%-----------ACHIEVEMENTS-----------
\section{Achievements \& Activities}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \large{\item{
     \textbf{Competitions}{: State Level Quiz Competition on Technical MCQ} \\
     \textbf{Hobbies}{: Reading, Writing, Learning Languages, Traveling} \\
    }}
 \end{itemize}


%-----------KNOWN LANGUAGES-----------
\section{Languages}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \large{\item{
     \textbf{Human Languages}{: English, Marathi, Hindi, German (A1 Level)} \\
    }}
 \end{itemize}

%-------------------------------------------
\end{document}