%-------------------------
% Tushar Patil Resume in Latex
% Author : Tushar Patil
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\large#3} & \textit{\large #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\large#1} & \textit{\large #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \large#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-2pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2pt}}

\setlength{\footskip}{4.08003pt}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}


\begin{center}
    \textbf{\Huge \scshape Tushar Patil} \\ \vspace{1pt}
    \large \href{tel:+919420955564}{\underline{+91 9420955564}} $|$ \href{mailto:patiltushar8084@gmail.com}{\underline{patiltushar8084@gmail.com}} $|$ 
    \href{https://github.com/tushar80}{\underline{github.com/tushar80}}
\end{center}


%-----------Summary-----------
\section{Summary}
    \textbf{Full Stack Developer} with \textbf{3+ years} of experience in \textbf{Python}, \textbf{React}, \textbf{GO}, and \textbf{AWS}. Proven track record in building scalable web applications. Passionate about delivering efficient and maintainable code.


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \large{\item{
     \textbf{Programming Languages}{: Python, JavaScript, C/C++, Go, SQL, TypeScript} \\
     \textbf{Frameworks}{: Django, Flask, ReactJS, Node.js} \\
     \textbf{Developer Tools}{: Linux, Amazon Web Services, Docker, Kubernetes, PostgreSQL} \\
     \textbf{Libraries}{: HTMX, pandas, NumPy}
    }}
 \end{itemize}
 

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer}{June 2022 -- Present}
      {Persistent Systems Ltd}{Pune, MH}
      \resumeItemListStart
        \resumeItem{Collaborated effectively in an \textbf{agile development} environment, consistently meeting deadlines and milestones while ensuring high-quality deliverables.}
        \resumeItem{Engaged directly with clients to discern and address feature requirements, fostering strong client relationships and delivering tailored solutions.}
        \resumeItem{Developed CRUD \textbf{REST APIs} using \textbf{DjangoRestFramework} and \textbf{PostgreSQL} for persistent data storage.}
        \resumeItem{Architected and implemented an \textbf{API authentication} module utilizing \textbf{OAuth}, ensuring secure access to application resources and protecting user data.}
        \resumeItem{Achieved a \textbf{20\%} reduction in AWS costs through strategic \textbf{cost optimizations}, optimizing resource allocation and enhancing cost efficiency for the client.}
        \resumeItem{Developed dynamic and responsive web applications using \textbf{React.js}, enhancing user experience with efficient and reusable components.}
        \resumeItem{Utilized \textbf{Axios} for seamless API integrations, ensuring reliable data fetching and handling in various project modules.}
        \resumeItem{Implemented robust state management solutions using \textbf{React hooks} and \textbf{context API} to maintain application state consistency.}
        \resumeItem{Implemented a billing feature in application using \textbf{AWS CostExplorer} API, streamlining client's invoicing process and improved financial visibility.}
        \resumeItem{Implemented fully customizable email and mobile notification service using \textbf{AWS SES} and \textbf{AWS SNS}.}
        \resumeItem{Implemented file sharing functionality on the web application using \textbf{AWS SES}.}
        \resumeItem{Collaborated closely with senior engineers to implement advanced file encryption using \textbf{AWS KMS}, enhancing data security and compliance measures.}
        \resumeItem{Collaborated with cross-functional teams and clients to gather requirements, troubleshoot issues, and optimize application performance.}
        \resumeItem{Engineered a seamless docx to PDF converter, enhancing user experience.}
        \resumeItem{Managed the \textbf{Kubernetes infrastructure} for deploying and scaling the application, ensuring high availability and reliability.}
        \resumeItem{Implemented \textbf{AWS CodePipeline} to streamline continuous delivery, automating the build, test, and deployment processes.}
        \resumeItem{Maintained and updated documentation for various components and modules, facilitating better team collaboration and onboarding processes.}
        \resumeItem{Wrote neat and clean \textbf{Unit Test cases}, ensuring robustness and reliability of the application.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Software Engineer Intern}{Jan. 2022 -- June 2022}
      {Persistent Systems Ltd}{Pune, MH}
      \resumeItemListStart
        \resumeItem{Collaborated with a team of 5 software engineers.}
        \resumeItem{Collaborated closely with senior team members to understand project requirements and translate them into actionable development tasks.}
        \resumeItem{Took ownership of small-scale projects or tasks, demonstrating initiative and accountability in project execution.}
        \resumeItem{Engaged in comprehensive code reviews, debugging, and troubleshooting sessions, actively contributing to codebase improvements and ensuring adherence to best practices.}
        \resumeItem{Acquired valuable hands-on experience with cutting-edge technologies including \textbf{Go}, \textbf{TypeScript}, and \textbf{Docker}, demonstrating adaptability and a willingness to learn new technologies.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Personal Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Bookera} $|$ \emph{JavaScript, NodeJS, React, PostgreSQL}}{}
          \resumeItemListStart
            \resumeItem{Developed a full-stack web application using with NodeJS serving a REST API with React as the frontend.}
            \resumeItem{Implemented features for writing book reviews and a rating system.}
            \resumeItem{Designed the database schema, implemented REST API endpoints, and documented the APIs.}
            \resumeItem{Integrated user authentication and authorization mechanisms using \textbf{JWT}.}
            \resumeItem{Implemented a search functionality to find books based on various criteria.}
            \resumeItem{Optimized frontend performance with React hooks and efficient state management.}
            \resumeItem{Utilized Git for version control and tracking changes in the codebase.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Team Task Manager} $|$ \emph{Python, Django, HTML/CSS, Git}}{}
          \resumeItemListStart
            \resumeItem{Developed a web application for managing tasks among teams with progress tracking feature.}
            \resumeItem{Published the app as django package on PyPI.}
            \resumeItem{Designed and implemented a user-friendly interface with HTML and CSS.}
            \resumeItem{Integrated email notifications for task updates and deadlines.}
            \resumeItem{Implemented role-based access control for different user types (e.g., admin, member).}
            \resumeItem{Utilized Git for version control and tracking changes in the codebase.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Sinhgad college of Engineering}{Solapur, MH}
      {Bachelor of Technology in Computer Science}{Aug. 2018 -- May 2022}
    \resumeSubheading
      {MIT junior college}{Solapur, MH}
      {HSC in Science}{Aug. 2016 -- May 2018}
  \resumeSubHeadingListEnd


%-----------Certifications-----------
\section{Certifications}
    \begin{itemize}
        \item \textbf{AWS Certified Developer - Associate}
    \end{itemize}


%-----------KNOWN LANGUAGES-----------
\section{Known Languages}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \large{\item{
     \textbf{Human Languages}{: English, Marathi, Hindi, German} \\
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
